Supplementary information for In-silico molecular transport via perivascular networks in the human intracranial space

### 2025-06-26 paper/supplementary.tex
Update title

\title{Supplementary information: In-silico molecular enrichment and clearance of the human intracranial space}
\author[1]{Marius Causemann}
\author[1]{Miroslav Kuchta}
\author[2]{Rami Masri}
\author[1,3,*]{Marie E. Rognes }
\affil[1]{Department of Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
\affil[2]{Division of Applied Mathematics, Brown University, Providence, Rhode Island, USA}
\affil[3]{K. G. Jebsen Centre for Brain Fluid Research, University of Oslo, Norway}
\affil[*]{meg@simula.no}

\begin{abstract}
  Supplementary methods and discussion accompanying the main text of
  \emph{In-silico molecular enrichment and clearance of the human
  intracranial space}.
\end{abstract}

>>>>

\title{Supplementary information for In-silico molecular transport via perivascular networks in the human intracranial space}
\author[1]{Marius Causemann}
\author[1]{Miroslav Kuchta}
\author[2]{Rami Masri}
\author[1,3,*]{Marie E. Rognes }
\affil[1]{Department of Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
\affil[2]{Division of Applied Mathematics, Brown University, Providence, Rhode Island, USA}
\affil[3]{K. G. Jebsen Centre for Brain Fluid Research, University of Oslo, Norway}
\affil[*]{meg@simula.no}

\begin{abstract}
  Supplementary methods and discussion accompanying the main text of
  \emph{In-silico molecular transport via perivascular networks in the human intracranial space}.
\end{abstract}
